Improvement of crash forces in structures using optimization tools.

### 2016-07-27 paper.tex
Avances

\documentclass[cmfonts]{witpress}
\usepackage{todonotes}
\usepackage{siunitx}
\usepackage{amsmath}
\usepackage{cleveref}
% \usepackage{natbib}
\bibliographystyle{witpress}

@@

\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.6\linewidth]{figures/IMG_CUTRES/medidas_cb}
	\caption{Dimensions of the modeled crash boxes, in millimeters. Taken from \cite{Peroni2009}.}
	\label{fig:crash_box}
\end{figure}

@@

The tube is crushed between two rigid plates, one fixed and the other moving at impact speed. In order to ease the formation of a stable collapse mechanism, a triggering is machined near the front end of the tube. The trigger starts a desired collapse mode in that area.

\subsubsection{Impact conditions} % Speed, etc
\label{sec:impact}

The tube was placed between two circular rigid plates, as it can be seen on \cref{fig:general}, one next to the impact head and the rear one next to the opposite end. The impact plate had a initial separation of $\SI{1}{\mm}$ to avoid simulation problems.

\begin{figure}
	\centering
	\begin{minipage}[b]{.22\linewidth}
		\centering
		\includegraphics[height=5cm]{figures/IMG_CUTRES/general_transp}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.22\linewidth}
		\centering
		\includegraphics[height=5cm]{figures/IMG_CUTRES/general_rigtransp}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.22\linewidth}
		\centering
		\includegraphics[height=5cm]{figures/IMG_CUTRES/general_noSb}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.22\linewidth}
		\centering
		\includegraphics[height=5cm]{figures/IMG_CUTRES/general_encastre}
	\end{minipage}
	\caption[General view of the model.]{General view of the model. Crushing from up to down. From left to right: view with transparency (adhesive in blue); view with rigid parts transparency; view without stabilizing box; view with the fixed part highlighted.}
	\label{fig:general}
\end{figure}

>>>>

\documentclass[cmfonts]{witpress}
\usepackage{todonotes}
\usepackage{siunitx}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{cleveref}
\usepackage{amssymb}
% \usepackage{natbib}
\bibliographystyle{witpress}

@@

\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.5\linewidth]{figures/IMG_CUTRES/medidas_cb}
	\caption{Dimensions of the modeled crash boxes, in millimeters. Taken from \cite{Peroni2009}.}
	\label{fig:crash_box}
\end{figure}

@@

The tube is crushed between two rigid plates, one fixed and the other moving at impact speed (see \Cref{fig:general}. In order to ease the formation of a stable collapse mechanism, a triggering is machined near the front end of the tube. The trigger starts a desired collapse mode in that area.

\begin{figure}[htpb]
	\centering
	\includegraphics[height=5cm]{figures/IMG_CUTRES/general_transp}
	\caption{General view of the model with the bounding box.}
	\label{fig:general}
\end{figure}
